Signal Processing to Demodulate FM Radio

### 2020-12-13 doc/paper/paper.tex
update

  \subsubsection{FM Channel Allocation}
    %https://www.electronics-notes.com/articles/audio-video/broadcast-audio/vhf-fm-frequency-modulation-basics.php
    The entire FM band frequency range divides into multiple channels which can be used.
    In Europe, the European Telecommunications Standards Institute (ETSI) sets the respective standards for the usage of these frequencies.
    The main specifications for a single FM broadcasting channels are explained in this section.
    Each channel may allocate a bandwidth of 200 kHz.
    Within a channel, the maximum deviation from the center frequency shall not exceed 75 kHz.
    This leaves a guard band of 25 kHz on either side, to minimize interference with adjacent channels.
    Center frequencies may be allocated on multiples of 100 kHz.
    %each channel:
    % spacing
    % bandwidth
    % specific part of spectrum (see Fig.1)
    % TODO: make Fig1 smaller (cut top/bottom)
    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-baseband.png}
      \caption{Allocation of frequencies in an FM channel}
      \label{fig_sim}
    \end{figure}

>>>>

  \subsubsection{FM Channel Allocation}
    %https://www.electronics-notes.com/articles/audio-video/broadcast-audio/vhf-fm-frequency-modulation-basics.php
    The entire FM band frequency range divides into multiple channels which can be used.
    In Europe, the European Telecommunications Standards Institute (ETSI) sets the respective standards for the usage of these frequencies.
    The main specifications for a single FM broadcasting channels are explained in this section.
    Each channel may allocate a bandwidth of 200 kHz.
    Within a channel, the maximum deviation from the center frequency shall not exceed 75 kHz.
    This leaves a guard band of 25 kHz on either side, to minimize interference with adjacent channels.
    Center frequencies may be allocated on multiples of 100 kHz.
    A sum of the left and right audio channel is located starting from 30 Hz, up to 15 kHz.
    The lower limit at 30 Hz is to prevent the transmission of a direct current (DC) part, which would require a large amount of power in transmission. This effect is one of the downsides of amplitude modulation (AM), where the carrier is located at the channels' center frequeny and requires a high transmission power. % TODO: check this fact
    The upper limit at 15 kHz is chosen, to maintain a sufficient spacing to the first subcarrier.
    This subcarrier is allocated at an offset of 19 kHz from the carrier.
    It is also called the 'pilot tone', since it is a continuous signal.
    The pilot tone is used to synchronize the left and right channel of an audio signal, to generate stereo audio.
    The center frequency for stereo audio is located at 38 kHz, which is an integer multiple of 19 kHz for practical reasons.
    A signal that is constructed of the difference between left and right audio channel is modulated on the 38 kHz subcarrier.
    The bandwidth for the difference-signal spans 15 kHz on either side.

    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-baseband.png}
      \caption{Allocation of frequencies in an FM channel}
      \label{fig_sim}
    \end{figure}
